|

### 2023-07-17 paper/04-results.Rmd
analysis of play context fixed effects

The results of fitting the multilevel model described in Section \ref{sec:multilevel} is displayed in Table \ref{tab:fixedeff}.
First, we investigate the fixed-effects terms of this model.
It appears that that the average STRAIN decreases by 0.042 (95% CI [-0.044, -0.040]) for every extra second in play length, and by 0.064 (95% CI [-0.069, -0.059]) every additional blocker in the offensive unit, after accounting for other covariates.
In other words, NFL pass rushers tend to generate more pressure in plays with shorter length (e.g., blitzes) and when facing fewer number of blockers, which makes intuitive sense.

Moreover, we observe statistically significant differences among the pass rush and pass block positions in most cases, while controlling for other variables.
The coefficient estimates for the pass rush position terms reveal that players with positions closer to the line of scrimmage (DTs and NTs) appear to generate less STRAIN (relative to DEs) than those lining up further back, which is consistent with our results in Section \ref{sec:positional}.
For blockers, centers are those that absorb the most pressure on average, more than guards and other offensive positions (compared to the baseline level, tackles).

@@

>>>>

The results of fitting the multilevel model described in Section \ref{sec:multilevel} is displayed in Table \ref{tab:fixedeff}.
First, we investigate the fixed-effects terms of this model.
It appears that that the average STRAIN decreases by 0.7366 (95% CI [-0.7875, -0.6858]) for every additional blocker in the offensive unit, after accounting for other covariates.
In other words, NFL pass rushers tend to generate more pressure when facing fewer number of blockers, which makes intuitive sense.

As for play context, defensive pressure appears to increase when more yardage is required for the offense to reach a first down and for later plays within a set of down, when all other predictors are held constant.
In particular, every extra yard in the distance needed for a first down is associated with a 0.0491 increase (95% CI [0.0426, 0.0555]) in the average STRAIN.
Relative to first down situations, higher amount of defensive pressure seem to happen in plays that come after (second, third, and fourth downs).
In addition, we have insufficient evidence for a relationship between average STRAIN and the current yardline on the field for the offensive team.

Moreover, we observe statistically significant differences among the pass rush and pass block positions in most cases, while controlling for other variables.
The coefficient estimates for the pass rush position terms reveal that players with positions closer to the line of scrimmage (DTs and NTs) tend to generate less STRAIN (relative to DEs) than those lining up further back, which is consistent with our results in Section \ref{sec:positional}.
For blockers, centers are those that absorb the most pressure on average, more than guards and other offensive positions (compared to the baseline level, tackles).

@@

[TODO: edit the above? McKinley still there but we did control for team effects]
